\section{\textbf{Leadership Experience}}
\vspace{-0.4mm}


% General Member - SGIPC
\begin{tabularx}{\textwidth}{X r} 
    \textbf{General Member} - Special Group Interested in Programming Contest (SGIPC) &
    \href{https://www.facebook.com/groups/sgipc.kuet/}{\textcolor{darkblue}{\faFacebook}} \\
\end{tabularx}
\vspace{-4mm}
\begin{itemize}
    \item Enhanced problem-solving and analytical skills by participating in competitive programming discussions.
    \item Developed communication, teamwork, and networking skills through collaboration with peers.
\end{itemize}

% Content and Training - LOOP, Control Engineering Club
\begin{tabularx}{\textwidth}{X r} 
    \textbf{Content and Training} - LOOP, Control Engineering Club &
    \href{https://www.facebook.com/kuetloop/}{\textcolor{darkblue}{\faFacebook}} \\
\end{tabularx}
\vspace{-4mm}
\begin{itemize}
    \item Developed training modules and created content for programming and control engineering education.
    \item Provided mentorship and leadership in training sessions for community engagement.
    \item Assisted in event coordination to foster learning and collaboration.
\end{itemize}

% Office Secretary - Save A Smile
\begin{tabularx}{\textwidth}{X r} 
    \textbf{Office Secretary} - Save A Smile &
    \href{https://www.facebook.com/groups/3109029409203422}{\textcolor{darkblue}{\faFacebook}} \\
\end{tabularx}
\vspace{-4mm}
\begin{itemize}
    \item A nonprofit organization run by students from different batches, dedicated to education, healthcare, and environmental sustainability.
    \item Oversaw the recruitment process, managing new member registrations and onboarding procedures.
    \item Maintained official records, meeting schedules, and internal documentation to ensure smooth organizational operations.
    \item Coordinated with various teams to plan and execute charity events, fundraising campaigns, and awareness programs.

\end{itemize}


% \vspace{-6mm}