\section{\textbf{Projects}}
\vspace{-0.4mm}

% Learnathon 3.0
% BanglaHire Project
\begin{tabularx}{\textwidth}{X r} 
    \textbf{BanglaHire} - Freelancing platform for Bangladesh &
    \textbf{February 2025 - May 2025} \quad 
    \href{https://github.com/Learnathon-By-Geeky-Solutions/bladerunners}{\textcolor{darkblue}{\faGithub}} \quad
    \href{https://bladerunners.proactive-coder.xyz/}{\textcolor{teal}{\faExternalLink*}} \\
\end{tabularx}
\vspace{-4mm}
\begin{itemize}
    \item Developed a full-stack freelancing platform using \textbf{Next.js} and \textbf{Laravel}, tailored for Bangladeshi freelancers and clients.
    \item Integrated \textbf{secure authentication}, \textbf{project bidding}, and \textbf{real-time messaging} with scalable backend logic.
    \item Implemented escrow payments via \textbf{SSLCommerz} and \textbf{Stripe}, ensuring secure transactions.
    \item Built an admin dashboard for user and transaction management; deployed using \textbf{Docker}.
    \item Applied static code analysis and quality monitoring through \textbf{SonarCloud}.
\end{itemize}


% Foodier Project
\begin{tabularx}{\textwidth}{X r} 
    \textbf{Foodier} - A dual iOS app project focused on a Food Management System &
    \textbf{September 2023 - January 2024} \quad \href{https://github.com/MachangDoniel/Foodier}{\textcolor{darkblue}{\faGithub}} \\
\end{tabularx}
\vspace{-4mm}
\begin{itemize}
    \item Designed an order queue management component, streamlining the processing of orders at various stages.
    \item Implemented Firebase Firestore for seamless data synchronization, achieving a 50\% faster order update time.
    \item Created a custom SwiftUI user interface, ensuring a visually appealing and intuitive user experience.
    \item Developed a dynamic HomeView system enabling personalized restaurant and menu exploration for users.
\end{itemize}

% KUET-BANK (Android)
\begin{tabularx}{\textwidth}{X r} 
    \textbf{KUET-BANK} - An Android project based on Bank Management System &
    \textbf{September 2022 - January 2023} \quad \href{https://github.com/MachangDoniel/KUET-BANK}{\textcolor{darkblue}{\faGithub}} \\
\end{tabularx}
\vspace{-4mm}
\begin{itemize}
    \item Developed a secure login and registration system with email verification and OTP authentication.
    \item Implemented a transaction management system for real-time user-to-user money transfers with minimal latency.
    \item Built a loan application and EMI payment system, streamlining financial operations for customers and admins.
\end{itemize}

% KUET-BANK (Web)
\begin{tabularx}{\textwidth}{X r} 
    \textbf{KUET-BANK} - A web-based Bank Management System &
    \textbf{February 2023 - February 2024} \quad \href{https://github.com/MachangDoniel/KUET-BANK}{\textcolor{darkblue}{\faGithub}} \\
\end{tabularx}
\vspace{-4mm}
\begin{itemize}
    \item Developed a secure login and registration system with email verification and OTP authentication.
    \item Implemented a transaction management system, processing real-time customer-to-customer transfers.
    \item Created an employee management dashboard for bank staff to manage customer accounts.
    \item Built an admin panel for data analysis and reporting.
\end{itemize}

% DoRa Block Battle
\begin{tabularx}{\textwidth}{X r} 
    \textbf{DoRa Block Battle} - An interactive AI-based game &
    \textbf{July 2022 - September 2022} \quad \href{https://github.com/MachangDoniel/DoRa-Block-Battle}{\textcolor{darkblue}{\faGithub}} \\
\end{tabularx}
\vspace{-4mm}
\begin{itemize}
    \item Developed an interactive game interface using Tkinter with single and multiplayer modes.
    \item Integrated AI algorithms (MinMax, Alpha-Beta Pruning, Genetic Algorithm, A*) for strategic gameplay.
    \item Designed adaptive gameplay that adjusts difficulty based on player actions.
    \item Conducted performance analysis to optimize AI decision-making efficiency.
\end{itemize}

% Heart (Cardiac Recorder)
\begin{tabularx}{\textwidth}{X r} 
    \textbf{Heart} - An Android application for patient heart rate data &
    \textbf{September 2021 - December 2021} \quad \href{https://github.com/MachangDoniel/Heart}{\textcolor{darkblue}{\faGithub}} \\
\end{tabularx}
\vspace{-4mm}
\begin{itemize}
    \item Developed an Android app to store and manage patient heart rate data.
    \item Integrated Firebase for real-time data storage and management.
    \item Implemented search functionality for patient record retrieval.
    \item Designed an intuitive user interface for seamless navigation.
\end{itemize}

% Night Security Light
\begin{tabularx}{\textwidth}{X r} 
    \textbf{Night Security Light} - An Arduino-based security system &
    \textbf{March 2022 - May 2022} \quad \href{https://github.com/MachangDoniel/Night_Security_Light}{\textcolor{darkblue}{\faGithub}} \\
\end{tabularx}
\vspace{-4mm}
\begin{itemize}
    \item Designed an automatic night security light system using Arduino Uno and motion sensors.
    \item Integrated a PIR sensor for movement detection and an LDR for ambient light measurement.
    \item Implemented a Bluetooth module for remote control of the system.
\end{itemize}

% Alphabet Detection
\begin{tabularx}{\textwidth}{X r} 
    \textbf{Alphabet-Detection} - An Image Processing project for detecting English alphabets &
    \textbf{March 2023 - October 2023} \quad \href{https://github.com/MachangDoniel/Alphabet-Detection}{\textcolor{darkblue}{\faGithub}} \\
\end{tabularx}
\vspace{-4mm}
\begin{itemize}
    \item Developed an image processing system to detect and recognize English alphabets.
    \item Implemented computer vision techniques to improve accuracy in alphabet identification.
    \item Optimized processing speed for real-time applications in text recognition.
\end{itemize}

% Automatic Bill Generator (KUET Teacher's Bill)
\begin{tabularx}{\textwidth}{X r} 
    \textbf{Automatic Bill Generator} - A desktop app for KUET teacher’s bill calculation &
    \textbf{September 2022 - December 2023} \quad \href{https://github.com/MachangDoniel/Automatic-Bill-Generator}{\textcolor{darkblue}{\faGithub}} \\
\end{tabularx}
\vspace{-4mm}
\begin{itemize}
    \item Built a desktop application to automate KUET teacher’s payment calculation based on their departmental activities.
    \item Designed a data-driven calculation engine to streamline the payment process.
    \item Integrated report generation for accurate payment summaries.
\end{itemize}

% Auto Birthday Wisher
\begin{tabularx}{\textwidth}{X r} 
    \textbf{Auto Birthday Wisher} - A Python program to send automatic birthday wishes &
    \textbf{January 2023 - February 2023} \quad \href{https://github.com/MachangDoniel/Auto-Birthday-Wisher}{\textcolor{darkblue}{\faGithub}} \\
\end{tabularx}
\vspace{-4mm}
\begin{itemize}
    \item Developed a Python script to automatically send birthday wishes via email or messaging apps.
    \item Integrated cron jobs and scheduling for timely execution.
    \item Used database storage for managing contact lists and birthdays.
\end{itemize}

% Hospital Management System
\begin{tabularx}{\textwidth}{X r} 
    \textbf{Hospital Management System} - A website for hospital management &
    \textbf{February 2023 - September 2023} \quad \href{https://github.com/MachangDoniel/Hospital_Management_System}{\textcolor{darkblue}{\faGithub}} \\
\end{tabularx}
\vspace{-4mm}
\begin{itemize}
    \item Developed a hospital management system using Laravel, PHP, MySQL, and Bootstrap.
    \item Implemented patient record management, appointment scheduling, and billing modules.
    \item Designed an admin panel for staff and hospital administrators to track hospital activities.
\end{itemize}

% Kokborok Compiler
\begin{tabularx}{\textwidth}{X r} 
    \textbf{Kokborok Compiler} - A compiler for the Kokborok(Tripura) language &
    \textbf{September 2021 - December 2021} \quad \href{https://github.com/MachangDoniel/Kokborok-Compiler}{\textcolor{darkblue}{\faGithub}} \\
\end{tabularx}
\vspace{-4mm}
\begin{itemize}
    \item Developed a compiler for the Kokborok language as part of a Compiler Design course.
    \item Implemented lexical analysis, syntax parsing, and semantic analysis.
    \item Designed a custom language structure to support various programming constructs.
\end{itemize}

\vspace{-2mm}
